Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
aws tabla instances

@@

\begin{itemize}
\item Esc\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/AWS.pdf}
  \caption{An AWS instance with 13 remote GPUs}
  \label{fig:aws1}
\end{figure}enarios creados

\item Experimentos
\item An\'alisis basados en flexibilidad y coste econ\'omico
\end{itemize}

>>>>

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{AWS Instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.4cm
\begin{center}\begin{tabular}{ccc}
Server & Client & BandWidth Gb/s\\ \hline \hline
g2.8xlarge & c3.2xlarge & 1 \\ \hline
g2.8xlarge & c3.8xlarge & 7.5 \\ \hline
g2.8xlarge & g2.2xlarge & 1 \\ \hline
g2.8xlarge & g2.8xlarge & 7.5 \\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{An AWS instance with several remote GPUs}
\label{fig:aws}
\end{figure*}

\begin{itemize}
\item Escenarios creados
\item Experimentos
\item An\'alisis basados en flexibilidad y coste econ\'omico
\end{itemize}
